Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-09-11 awipev-CO2.Rmd
first modification concerning SNAPO part's plots

```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d_all %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))
 diff <- d_all %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))

>>>>

```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))
